---
title: "R Notebook"
output: html_notebook
---

# The aim here is to create new features that measures popularity and engagement

## Basic setup

```{r libraries_glob_vars}
library('tidyverse')
library('tidytext')
library('anytime')
```

Read data. and convert columns into correct formats.
```{r read_data}
df_raw <- read_csv('../data/raw/ted_main.csv')
head(df_raw)
```

Convert columns into correct formats.
```{r convert_columns}
df <- df_raw %>%
  mutate_at(funs(anydate(., tz = 'UTC')), .vars = c('film_date', 'published_date'))

```


How many views per period of time since release? The data set is until September 21st, 2017.

What is the distribution of time since release?
```{r days_since_release}
# The data set is until September 21st, 2017.
final_date <- as.Date('2017-09-21')

df <- df %>%
  mutate(days_since_release = final_date - published_date)

ggplot(df, aes(log(as.integer(days_since_release)))) +
  geom_density()

ggplot(df, aes(as.integer(days_since_release))) +
  geom_density()

```

So there were quite a few talks released close to the cutoff date of data collection.

```{r filter_time_from_release}
df_filt_release_date <- df %>%
  filter(days_since_release > 356)
```

## Popularity

```{r popularity}
df_pop <- df_filt_release_date %>%
  mutate(popularity = views / as.integer(days_since_release)) %>%
  select(popularity, title)

ggplot(df_pop, aes(popularity)) +
  geom_density()
```

## By engangement

We call engagement the number of comments per view. The more number of comments, then the more engaging the video is.

```{r engagement}
df_engagement <- df_filt_release_date %>%
  mutate(engagement = comments / views ) %>%
  select(title, engagement)

df_engagement %>%
  ggplot(aes(engagement)) +
  geom_density()

```

Compare how the metrics of popularity, engagement and views stack up.

```{r compare_popularity_engagement_views}
cutoff = 20 # (top n)
df_comparisons <- df_pop %>%
  left_join(df_engagement, by = 'title') %>%
  left_join(df_filt_release_date, by = 'title') %>%
  mutate(popularity_rank = rank(-popularity)) %>%
  mutate(views_rank = rank(-views)) %>%
  mutate(engagement_rank = rank(-engagement)) %>% ## should be a quicker way, probably mutate_at
  filter(views_rank <= cutoff | popularity_rank <= cutoff | engagement_rank <= cutoff) 

ggplot(df_comparisons, aes(views, popularity)) +
  geom_point()

ggplot(df_comparisons, aes(views, engagement)) +
  geom_point()

```
